Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2021-01-02 main_new.tex
Updates from Overleaf

\documentclass[aoas]{imsart}

@@

\subsubsection{Including Spatiality}

@@

\begin{figure}[ht] 
\centering 
\subfigure[Excursion probability.]{\includegraphics[
height=0.25\textwidth,keepaspectratio]{Figures/ebv_static_excu.png}\label{fig:ebv_static_excu}}
\subfigure[Static north design.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_static_north.png}\label{fig:ebv_static_north}}
\subfigure[Static east design.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_static_east.png}\label{fig:ebv_static_east}}
\hspace{2em}
\subfigure[Excursion realization.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/real_myopic.png}\label{fig:real_myopic}}
\hspace{2em}
\subfigure[Route taken by myopic strategy.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/route_myopic.png}\label{fig:route_myopic}}
\hspace{2em}
\subfigure[Directional reduction of EBV.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/compass_myopic.png}\label{fig:compass_myopic}}
\caption{Pointwise Bernoulli variance reduction for two static and the myopic observation strategies. The prior EP is shown in
  \ref{fig:ebv_static_excu}. EBV reduction for each design shown in
  \ref{fig:ebv_static_north} and \ref{fig:ebv_static_east}. The true excursion for a realization of temperature and salinity is shown in \ref{fig:real_myopic}. The route taken by the myopic observation strategy is shown in \ref{fig:route_myopic}. The different alternative route choices and their expected EBV, illustrated as a compass from the perspective of the AUV, is shown in \ref{fig:compass_myopic}. Southward or $270 ^{\circ}$ is indicated by the thick and light color to be the best alternative direction.}
\label{fig:ebv_north_vs_east}
\end{figure}

@@

>>>>

\documentclass[aoas,preprint]{imsart}
\setattribute{journal}{name}{}

@@

\subsubsection{Including Spatiality}
\label{sec:including_spatiality}

@@

\begin{figure}[ht] 
\centering 
\subfigure[Excursion probability.]{\includegraphics[
height=0.25\textwidth,keepaspectratio]{Figures/ebv_static_excu.png}\label{fig:ebv_static_excu}}
\subfigure[Static north design.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_static_north.png}\label{fig:ebv_static_north}}
\subfigure[Static east design.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_static_east.png}\label{fig:ebv_static_east}}
\caption{Pointwise Bernoulli variance reduction for two different static designs (later noted as \textit{static\_north} and \textit{static\_east}). The prior EP is shown in
  \ref{fig:ebv_static_excu}. EBV reduction for each design shown in
  \ref{fig:ebv_static_north} and \ref{fig:ebv_static_east}.}
\label{fig:ebv_north_vs_east}
\end{figure}

@@

\begin{figure}[ht] 
\centering 
\subfigure[Excursion realization.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_myopic_excu.png}\label{fig:real_myopic}}
\hspace{2em}
\subfigure[BV reduction.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_myopic_ebv.png}\label{fig:route_myopic}}
\hspace{2em}
\subfigure[Expected reduction of BV.]{\includegraphics[
height=0.26\textwidth,keepaspectratio]{Figures/ebv_myopic_radar.png}\label{fig:compass_myopic}}
\caption{Example run of the myopic strategy on a given realisation of the GRF model from \ref{sec:including_spatiality}. Past observation locations are depicted in green and current position of the AUV in cyan. The expected EBV reduction associated to data collection at neighbouring nodes of the current location is shown in \ref{fig:compass_myopic}. The thick and light color indicate the north-east node at $30 ^{\circ}$ to be the best possible choice.}
\label{fig:ebv_myopic}
\end{figure}
